\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}

\geometry{left=1in, right=1in, top=1in, bottom=1in}

\begin{document}

\begin{center}
    \textbf{\LARGE Satoru Gojo} \\
    \vspace{0.2cm}
    Tokyo Prefectural Jujutsu High School • Minato City, Minamiaoyama, 5-7-2 • Tokyo, Japan 107-0062 \\
    \href{mailto:sgojo@jjk.edu.jp}{sgojo@jjk.edu.jp} • @sgojo • \href{http://sgojo.jjk.com}{sgojo.jjk.com} • Updated: June 15, 2024
\end{center}

\vspace{0.5cm}

\section*{Current Position}
\textbf{Tokyo Prefectural Jujutsu High School} \hfill Tokyo, Japan \\
Faculty \hfill Jul. 2010 - Present

\vspace{0.5cm}

\section*{Education}
\textbf{Tokyo Prefectural Jujutsu High School} \hfill Tokyo, Japan \\
Special Grade Jujutsu Sorcerer \hfill Jul. 2006 - 2010 \\
\begin{itemize}
    \item \textbf{Trait and Technique:} The Six Eyes (Rikugan), Limitless (Mukagen), Infinity (Mugen).
    \item \textbf{Cursed Technique:} Cursed Technique Lapse: Blue (Jutsubshiki Junten Ao), Cursed Technique Reversal: Red (Jutsubshiki Hanten Aka), Hollow Technique: Purple (Kyoshiki Murasaki).
    \item \textbf{Domain Expansion:} Unlimited Void (Muryokushō).
\end{itemize}

\vspace{0.5cm}

\section*{Project}
\textbf{Fight against Ryomen Sukuna} \hfill Jun. 2023 - Present \\
Main Challenger
\begin{itemize}
    \item The complete incapacitation of the target is caused by a phenomenon where the target will be able to see and feel everything while not being able to see or feel anything at the same time.
    \item All the actions one has taken in their life is forced upon them infinitely and they can’t do anything but die slowly, though this effect does not affect Gojo or anyone he’s touching.
    \item Even though his title of ‘The Strongest’ is self-proclaimed, most allies and enemies alike never actually dispute the title and consider him one of the most dangerous people alive.
\end{itemize}

\vspace{0.5cm}

\textbf{My Dress-Up Darling} \hfill May 2024 - Present \\
Outfit to Yuta Okkotsu
\begin{itemize}
    \item Okkotsu is barely alive and Rika is able to take him to Ieiri’s team, when he decides to go forward with his prior agreement with Gojo to use Kenjaku’s technique and take over Gojo’s corpse to fight Sukuna again, saving Yuji and Todo from the latter’s Domain Expansion, by initiating Gojo’s.
    \item After several exchanges, Gojo defeats all of the Ten Shadows that Sukuna used and greatly injures him, but ends up being killed by Sukuna’s new World Cutting technique and finds himself talking with Geto and his other late friends. Gojo’s corpse is then used by Okkotsu with Kenjaku’s technique, as per their previous agreement.
\end{itemize}

\vspace{0.5cm}

\section*{Misc}
\textbf{Voiced by:} Yuichi Nakamura, Mariya Ise (young) (Japanese); Kaiji Tang, Cristina Vee (young) (English). \\
\textbf{Students:} Yuji Itadori, Yuta Okkotsu.

\end{document}
